%!TEX TS-program = xelatex
\documentclass[backend=biber, print]{friggeri-cv}
\addbibresource{bibliography.bib}

\begin{document}
\header{erkhembayar}{gantulga}
       {web developer}


% In the aside, each new line forces a line break
\begin{aside}
  \section{about}
    5 rue de la Fidelite
    75010 Paris
    France
    \href{mailto:erheme318@gmail.com}{erheme318@gmail.com}
    \href{http://erheme318.wordpress.com}{erheme318.wp.com}
    \href{http://github.com/erheme318}{}
  \section{languages}
    mongolian native
    english fluency
    czech notions
    french
  \section{programming}
    {\color{red} $\varheartsuit$} PHP (Symfony1\&2)
    JavaScript, Shell, Java, Linux
    Mysql, Git, Subversion, Vim
  \section{certificates}
    IBM Websphere Message Broker V7.0, Solution Developer
\end{aside}

\section{interests}

Machine learning, Data analysis, Algorithm, Chess, History, Photography
\section{education}

\begin{entrylist}
  \entry
    {2011–2014}
    {M.Eng.}
    {University of Hradec Kralove}
    {Majoring in Information Management}
  \entry
    {2005–2009}
    {B.Sc. magna cum laude}
    {Mongolian State University of Agriculture}
    {Majoring in Computer Science}
  \entry
    {2005}
    {Highschool}
    {School number 32, Ulaanbaatar}
    {Specialization in mathematics}
\end{entrylist}

\section{experience}

\begin{entrylist}
  \entry
    {09–12 2013}
    {La Ruche qui dit Oui !}
    {Internship}
    {\emph{Web application development}}
  \entry
    {02–07 2013}
    {NTUST, Taipei}
    {Exchange student.}
    {\emph{Machine Learning, Computation Photography, AI, Visual Servo Control.}}
  \entry
    {10 2012 –02 2013}
    {IBM Czech Republic, Praha}
    {Frontend engineer.}
    {\emph{Cloud service implementation project}}
  \entry
    {06–09 2012}
    {IBM Czech Republic, Praha}
    {Research Internship.}
    {\emph{System Integration Developer}}
  \entry
    {08 2010–08 2011}
    {Singleton LLC, Ulaanbaatar}
    {Web developer.}
    {\emph{E-commerce, Web application development}}
  \entry
    {09 2009–08 2010}
    {Dayar Group LLC, Ulaanbaatar}
    {Web developer.}
    {\emph{B2B web application development.}}
\end{entrylist}

\section{applications}

\begin{entrylist}
  \entry
    {since 2011}
    {Mongolian news portal}
    {\href{http://terguulegch.com}{terguulegch.com}}
    {News, Language, Cultural portal for Mongolian community in Europe.}
  \entry
    {2012}
    {Mongolian Mining Supply Chain Database}
    {\href{http://miningsupply.bcm.mn}{miningsupply.bcm.mn}}
    {Mining supply chain database provides recent tenders, events and provider companies information }
  \entry
    {2011}
    {La ruche qui dit oui!}
    {\href{http://www.laruchequiditoui.fr}{laruchequiditoui.fr}}
    {B2B e-commerce platform}
  \entry
    {2011}
    {Mongolfood.mn!}
    {\href{http://mongolfood.mn/}{mongolfood.mn}}
    {E-commerce system development}
  \entry
    {2010}
    {Mongolia Mining Value Chain}
    {\href{http://mining-valuechain.eri.mn}{mining-valuechain.mn}}
    {Mining Value Chain Project in Mongolia | The World Bank}
  \entry
    {2010}
    {Norway B2C, C2C online e-commerce system.}
    {\href{http://dev.yozoa.com}{yozoa.com}}
    {Developed new features (e.g. Location based and product search),  in existing system.}
  \entry
    {2010}
    {Information system of National Influenza Center.}
    {}
    {System maintenance development}
  \entry
    {2010}
    {National Air Traffic Services.}
    {\href{http://nats.mcaa.gov.mn/}{nats.mcaa.gov.mn}}
    {Web based system development of National Air Traffic Services of the Civil Aviation Authority of Mongolia.}
  \entry
    {2009-2010}
    {Dayar B2B system.}
    {}
    {Web system development and administration of B2B portal site for more than 50 industries of Mongolia.}
\end{entrylist}

\section{publications}

\begin{refsection}
  \nocite{*}
    \printbibliography[sorting=chronological, type=inproceedings, title={international peer-reviewed conferences/proceedings}, notkeyword={france}, heading=subbibliography]
    \end{refsection}

\end{document}
